# Imports

```{r}
library(dplyr)
library(GenomicRanges)
library(intSiteRetriever)
library(hiAnnotator)
library(BSgenome)
```

# Data Wrangling

Lets load reference genome:
```{r}
referenceGenome <- "hg18"
reference <- get_reference_genome(referenceGenome)
```

Cell type and genomic location data:
```{r}
cellType_location <- read.csv("fdr-empir.csv")
columns <- c("Neutrophil", "Bcell", "Tcell", "Monocytes", "NKcell", "location")
cell_location <- select(cellType_location, one_of(columns)) 
# TEMP FOR DEVELOPMENT
cell_location <- sample_frac(cell_location, 0.05)
```

For each cell type we need to get genomic locations of sites:
```{r}
cell_types <- c("Neutrophil", "Bcell", "Tcell", "Monocytes", "NKcell")
sites_for_cell_type <- lapply(cell_types, function(cell_type) {
    cell_type_present <- filter_(cell_location, paste(cell_type, " > 0"))
    data_frame(location=cell_type_present$location, label=cell_type) 
})
sites <- do.call(rbind, sites_for_cell_type)
```

Create genomic ranges object and add metadata for heatmaps:
```{r}
sites$type <- "insertion" # real integration event
sites$siteID <- seq(1, nrow(sites))
sites_meta <- sites[c("siteID", "label", "type")]
sites <- GRanges(sites$location, seqinfo = seqinfo(reference))
mcols(sites) <- sites_meta
```

Now we need to create several(N_MRCs) matched random controls:
```{r}
N_MRCs <- 3
siteIDs <- sites$siteID
mrcs <- get_random_positions(siteIDs, reference, number_of_positions = N_MRCs)
mrcs$label <- rep(sites$label, each=N_MRCs)
mrcs$type <- "match"
mrcs$location <- paste0(mrcs$chr, ":", mrcs$position, "-", mrcs$position, ":", mrcs$strand)
mrcs_meta <- mrcs[c("siteID", "label", "type")]
mrcs <- GRanges(mrcs$location, seqinfo=seqinfo(reference))
mcols(mrcs) <- mrcs_meta
```

Now we have real sites and controls and required metadata. 'SiteID' to link
sites and controls, 'type' to distiunguish them and 'label' for final labeling on 
plot:
```{r}
sites_mrcs <- c(sites, mrcs)
```


# Genomic Heatmap

# Epigenetic Heatmap

